---
title: "Sub-corpus creation: Social Inequality and Care (SIC)"
---
# Load necessary packages
```{r include=FALSE}
# Package names
packages <- c("dplyr", "stringr", "readr", "parallel")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

```

# MAIN STRING to search for: get doc_ids of articles with match
```{r 1}
# Construct a search string, which will use single and multi-word expressions
# Since we are using a lemmatized corpus, we need to use lemmas instead of words
sic_search_string <-
  c(
"chudoba",
"hmotná nouze",
"chudá domácnost",
"hmotná nouze",
"bezdomovectví",
"bezdomovec",
"lidé bez domova",
"člověk bez domova",
"člověk bez přístřeší",
"sociální vyloučení",
"sociální začleňování",
"znevýhodněná osoba",
"znevýhodněné osoby",
"bytová nouze",
"sociální dávky"
    # We add regex word boundaries \\b to avoid matching substrings
    # e.g. "klimatický" would match "klimatickým" and "klimatickými" otherwise
    # Also, we collapse the vector into a single string, which is separated by the OR operator |
    # The resulting string is then used in the str_detect() function
    # The ideas is to detect the presence of at least one of the expressions in the string
    # Such a document is then considered to be a "SIC article"
  )  %>% str_c("\\b", ., "\\b", collapse = "|") 

# Identify UPIPE-processed chunks of interest
path_to_input_udpipe <- "~/Rprojekt/Climate/2.data_transformations/data/udpipe_processed"
udpipe_chunks_path <-
  list.files(
    path = file.path(path_to_input_udpipe),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify a function to extract doc_ids of articles with match
get_sic_articles <- function(udpipe_chunk_path) {
  tryCatch({
    readRDS(udpipe_chunk_path) %>%
      mutate(doc_id,
             text = str_to_lower(lemma, locale = "cs"),
             .keep = "none") %>%
      group_by(doc_id) %>%
      summarize(
        text = str_flatten(text, collapse = " ", na.rm = TRUE),
        sic_string_matches = str_c(unlist(
          str_extract_all(text, sic_search_string)
        ), collapse = " | ")
      ) %>%
      ungroup() %>%
      filter(nchar(sic_string_matches) > 0) %>%
      select(doc_id, sic_string_matches)
  }, error = function(e) {
    message("Error processing file: ", udpipe_chunk_path)
    message("Error message: ", e$message)
    return(NULL)
  })
}

```

# Iterate over the list of UDPIPE chunks and extract all of the documents that match the search string
```{r 2}
if (Sys.info()[['sysname']] == "Windows") {
sic_article_ids <- lapply(udpipe_chunks_path, get_sic_articles) %>% bind_rows()
} else {
sic_article_ids <- mclapply(udpipe_chunks_path, get_sic_articles,  mc.cores = detectCores() - 2) %>% bind_rows()
}

saveRDS(sic_article_ids, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_article_ids.rds")
```

# Possibly FILTER manually labelled articles: get doc_ids to filter out
```{r 3}
# Manually labelled sub-corpus SIC v2
# The column "your_notes" contains "x" for articles, which are not relevant for the sub-corpus
# We want to get the "doc_id" of these articles and filter them out from the sub-corpus SIC
get_doc_ids_to_filter <- function(file_path, filter_by) {
  # Load the manually labelled sub-corpus SIC, which is already downloaded from a repository
  sic_corpus_v2_labelled <- readr::read_delim(file_path, delim = "\t", quote = "none")
  
  # Handle potential parsing issues
  parsing_problems <- readr::problems(sic_corpus_v2_labelled)
  
  if (nrow(parsing_problems) > 0) {
    warning("There were problems parsing the file. Call `problems(sic_corpus_v2_labelled)` for details.")
  }
  
  # Filter by pattern of interest on the column of interest
  doc_ids_to_filter <- dplyr::filter(sic_corpus_v2_labelled, stringr::str_detect(your_notes, filter_by)) %>%
    dplyr::pull(article_id)
  
  return(doc_ids_to_filter)
}
# Load the manually labelled dataset and get the doc_ids of articles to filter out
doc_ids_to_remove <- get_doc_ids_to_filter("/Users/IreneE/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_corpus_v2_labelled.csv", filter_by = "^x")
saveRDS(doc_ids_to_remove, "/Users/IreneE/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_doc_ids_to_remove.rds")
```

#Final step: Export sub-corpus with texts to upload to Google Sheets for manual annotation and review, while filtering out the articles, which were already manually labelled as irrelevant in the sub-corpus V2.
```{r 4}
sic_article_ids <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_article_ids.rds")
doc_ids_to_remove <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_doc_ids_to_remove.rds")

path_to_input_regex <- "~/Rprojekt/Climate/2.data_transformations/data/regex_processed"
regex_chunks_path <-
  list.files(
    path = file.path(path_to_input_regex),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify function, which will extract the texts of interest based on relevant doc_ids
get_sic_texts <-
  function(regex_chunk_path,
           #doc_ids_to_remove,
           sic_article_ids) {
    regex_chunk_path %>%
      readRDS() %>%
      #filter(!article_id %in% doc_ids_to_remove) %>%
      inner_join(sic_article_ids, by = c("article_id" = "doc_id"))
  }
```

# Iterate over the list of Regex chunks and get all of the relevant texts
```{r 5}
if (Sys.info()[['sysname']] == "Windows") {
  sic_corpus  <-
    lapply(regex_chunks_path, function(x)
      get_sic_texts(x, sic_article_ids)) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
} else {
  # If not Linux - non-parallelized lapply
  sic_corpus <-
    mclapply(regex_chunks_path, function(x)
      get_sic_texts(x, sic_article_ids),  mc.cores = detectCores() - 2) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
}

# Save final SIC sub-corpus
saveRDS(sic_corpus, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_corpusv2.rds")
```

# Prepare the file for Google Sheets upload
```{r 6}
# We probably need to observe the Google Sheets 50k character limit, otherwise the text of the article will not appear at all.
sic_corpus_truncated <- sic_corpus %>% 
  mutate(text = str_trunc(str_squish(text), width = 49997, side = "right", ellipsis = "..."))
  
# Save the sub-corpus to a CSV file, which we upload to Google Sheets for manual annotation and review
write_csv(sic_corpus_truncated, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_articles_v2_truncated.csv")

```
## Eviction and monetary execution
```{r Ex1}
#Extra chunk to reveal in how many articles there are these three eviction-related words:
# Construct a search string, which will use single and multi-word expressions
# Since we are using a lemmatized corpus, we need to use lemmas instead of words
execution_search_string <-
  c(
"exekuce",
"exekutor",
"exekutorský"
    # We add regex word boundaries \\b to avoid matching substrings
    # e.g. "klimatický" would match "klimatickým" and "klimatickými" otherwise
    # Also, we collapse the vector into a single string, which is separated by the OR operator |
    # The resulting string is then used in the str_detect() function
    # The ideas is to detect the presence of at least one of the expressions in the string
    # Such a document is then considered to be a "SIC article"
  )  %>% str_c("\\b", ., "\\b", collapse = "|") 

# Identify UPIPE-processed chunks of interest
path_to_input_udpipe <- "~/Rprojekt/Climate/2.data_transformations/data/udpipe_processed"
udpipe_chunks_path <-
  list.files(
    path = file.path(path_to_input_udpipe),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify a function to extract doc_ids of articles with match
get_execution_articles <- function(udpipe_chunk_path) {
  tryCatch({
    readRDS(udpipe_chunk_path) %>%
      mutate(doc_id,
             text = str_to_lower(lemma, locale = "cs"),
             .keep = "none") %>%
      group_by(doc_id) %>%
      summarize(
        text = str_flatten(text, collapse = " ", na.rm = TRUE),
        execution_string_matches = str_c(unlist(
          str_extract_all(text, execution_search_string)
        ), collapse = " | ")
      ) %>%
      ungroup() %>%
      filter(nchar(execution_string_matches) > 0) %>%
      select(doc_id, execution_string_matches)
  }, error = function(e) {
    message("Error processing file: ", udpipe_chunk_path)
    message("Error message: ", e$message)
    return(NULL)
  })
}

```

# Iterate over the list of UDPIPE chunks and extract all of the Ex documents that match the search string
```{r Ex2 To get the execution articles}
if (Sys.info()[['sysname']] == "Windows") {
execution_article_ids <- lapply(udpipe_chunks_path, get_execution_articles) %>% bind_rows()
} else {
execution_article_ids <- mclapply(udpipe_chunks_path, get_execution_articles,  mc.cores = detectCores() - 2) %>% bind_rows()
}

saveRDS(execution_article_ids, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/execution_article_ids.rds")
```

# Possibly FILTER manually labelled articles: get doc_ids to filter out Ex files
```{r Ex3}
# Manually labelled sub-corpus SIC v2
# The column "your_notes" contains "x" for articles, which are not relevant for the sub-corpus
# We want to get the "doc_id" of these articles and filter them out from the sub-corpus SIC
get_doc_ids_to_filter <- function(sic_corpus_v2_labelled, filter_by) {
  # Load the manually labelled sub-corpus SIC, which is already downloaded from a repository
  sic_corpus_v2 <- read_csv(sic_corpus_v2_labelled, col_types = "cccc")
  # Filter by pattern of interest on the column of interest
  doc_ids_to_filter <- sic_corpus_v2 %>%
    mutate(your_notes = str_to_lower(your_notes, locale = "cs")) %>%
    filter(str_detect(your_notes, filter_by)) %>%
    pull(article_id)
  
  return(doc_ids_to_filter)
}
# Load the manually labelled dataset and get the doc_ids of articles to filter out
doc_ids_to_remove <- get_doc_ids_to_filter("~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/sic_corpus_v2_labelled.csv", filter_by = "^x")
saveRDS(doc_ids_to_remove, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/doc_ids_to_remove.rds")
```

# Final step for datasheet creation: Export sub-corpus with texts to upload to Google Sheets for manual annotation and review, while filtering out the articles, which were already manually labelled as irrelevant in the sub-corpus V2.
```{r Ex4}
execution_article_ids <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/execution_article_ids.rds")
#doc_ids_to_remove <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/doc_ids_to_remove.rds")

path_to_input_regex <- "~/Rprojekt/Climate/2.data_transformations/data/regex_processed"
regex_chunks_path <-
  list.files(
    path = file.path(path_to_input_regex),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify function, which will extract the texts of interest based on relevant doc_ids
get_execution_texts <-
  function(regex_chunk_path,
           #doc_ids_to_remove,
           execution_article_ids) {
    regex_chunk_path %>%
      readRDS() %>%
      #filter(!article_id %in% doc_ids_to_remove) %>%
      inner_join(execution_article_ids, by = c("article_id" = "doc_id"))
  }

```

# Iterate over the list of Regex chunks and get all of the relevant texts
```{r Ex5 Get the texts}
if (Sys.info()[['sysname']] == "Windows") {
  execution_corpus  <-
    lapply(regex_chunks_path, function(x)
      get_execution_texts(x, execution_article_ids)) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
} else {
  # If not Linux - non-parallelized lapply
  execution_corpus <-
    mclapply(regex_chunks_path, function(x)
      get_execution_texts(x, execution_article_ids),  mc.cores = detectCores() - 2) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
}

# Save final Ex sub-corpus
saveRDS(execution_corpus, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/execution_corpus.rds")
#Count articles
unique_article_ids <- length(unique(execution_corpus$article_id))
3379
```

# Prepare the file for datasheets upload
```{r Ex6 Prepare the file for datasheet upload}

# We probably need to observe the Google Sheets 50k character limit, otherwise the text of the article will not appear at all.
execution_corpus_truncated <- execution_corpus %>% 
  mutate(text = str_trunc(str_squish(text), width = 49997, side = "right", ellipsis = "..."))
  
# Save the sub-corpus to a CSV file, which we upload to Google Sheets for manual annotation and review
write_csv(execution_corpus_truncated, "~/Rprojekt/Climate/2.data_transformations/data/sic_sub_corpus/execution_articles_truncated.csv")
```

# We want to add some comparison subcorpora.

```{r Terrorist corpus}
# Construct a search string, which will use single and multi-word expressions
# Since we are using a lemmatized corpus, we need to use lemmas instead of words.
 # We add regex word boundaries \\b to avoid matching substrings
    # Also, we collapse the vector into a single string, which is separated by the OR operator |
    # The resulting string is then used in the str_detect() function
    # The ideas is to detect the presence of at least one of the expressions in the string
    # Such a document is then considered to be a "terrorist article"
  
terror_search_string <-
  c("terorismus", "teroristický", "terorista", "protiteroristický"
   )  %>% str_c("\\b", ., "\\b", collapse = "|") 

# Identify UPIPE-processed chunks of interest
path_to_input_udpipe <- "~/Rprojekt/Climate/2.data_transformations/data/udpipe_processed"
udpipe_chunks_path <-
  list.files(
    path = file.path(path_to_input_udpipe),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify a function to extract doc_ids of articles with match
get_terror_articles <- function(udpipe_chunk_path) {
  tryCatch({
    readRDS(udpipe_chunk_path) %>%
      mutate(doc_id,
             text = str_to_lower(lemma, locale = "cs"),
             .keep = "none") %>%
      group_by(doc_id) %>%
      summarize(
        text = str_flatten(text, collapse = " ", na.rm = TRUE),
        terror_string_matches = str_c(unlist(
          str_extract_all(text, terror_search_string)
        ), collapse = " | ")
      ) %>%
      ungroup() %>%
      filter(nchar(terror_string_matches) > 0) %>%
      select(doc_id, terror_string_matches)
  }, error = function(e) {
    message("Error processing file: ", udpipe_chunk_path)
    message("Error message: ", e$message)
    return(NULL)
  })
}

```
# Iterate over the list of UDPIPE chunks and extract all of the documents that match the search string
```{r 2}
if (Sys.info()[['sysname']] == "Windows") {
terror_article_ids <- lapply(udpipe_chunks_path, get_terror_articles) %>% bind_rows()
} else {
terror_article_ids <- mclapply(udpipe_chunks_path, get_terror_articles,  mc.cores = detectCores() - 2) %>% bind_rows()
}

saveRDS(terror_article_ids, "~/Rprojekt/Climate/2.data_transformations/data/terror_sub_corpus/terror_article_ids.rds")
```

#Final step: Export sub-corpus with texts to upload to Google Sheets for manual annotation and review, while filtering out the articles, which were already manually labelled as irrelevant in the sub-corpus V2.
```{r 4}
terror_article_ids <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/terror_sub_corpus/terror_article_ids.rds")
path_to_input_regex <- "~/Rprojekt/Climate/2.data_transformations/data/regex_processed"
regex_chunks_path <-
  list.files(
    path = file.path(path_to_input_regex),
    pattern = "*.rds",
    full.names = TRUE
  )

# Specify function, which will extract the texts of interest based on relevant doc_ids
get_terror_texts <-
  function(regex_chunk_path,
           #doc_ids_to_remove,
           terror_article_ids) {
    regex_chunk_path %>%
      readRDS() %>%
      #filter(!article_id %in% doc_ids_to_remove) %>%
      inner_join(terror_article_ids, by = c("article_id" = "doc_id"))
  }
```

# Iterate over the list of Regex chunks and get all of the relevant texts
```{r 5}
if (Sys.info()[['sysname']] == "Windows") {
  terror_corpus  <-
    lapply(regex_chunks_path, function(x)
      get_terror_texts(x, terror_article_ids)) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
} else {
  # If not Linux - non-parallelized lapply
  terror_corpus <-
    mclapply(regex_chunks_path, function(x)
      get_terror_texts(x, terror_article_ids),  mc.cores = detectCores() - 2) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
}

# Save final SIC sub-corpus
saveRDS(terror_corpus, "~/Rprojekt/Climate/2.data_transformations/data/terror_sub_corpus/terror_corpusv2.rds")
```
# Prepare the file for Google Sheets upload
```{r 6}
# We probably need to observe the Google Sheets 50k character limit, otherwise the text of the article will not appear at all.
terror_corpus_truncated <- terror_corpus %>% 
  mutate(text = str_trunc(str_squish(text), width = 49997, side = "right", ellipsis = "..."))
  
# Save the sub-corpus to a CSV file, which we upload to Google Sheets for manual annotation and review
write_csv(terror_corpus_truncated, "~/Rprojekt/Climate/2.data_transformations/data/terror_sub_corpus/terror_articles_v2_truncated.csv")
```
# A motorists corpus
```{r Motorist corpus}
# Construct a search string, which will use single and multi-word expressions
# Since we are using a lemmatized corpus, we need to use lemmas instead of words.
 # We add regex word boundaries \\b to avoid matching substrings
  # Also, we collapse the vector into a single string, which is separated by the OR operator |
  # The resulting string is then used in the str_detect() function
  # The ideas is to detect the presence of at least one of the expressions in the string
  # Such a document is then considered to be a "motorist article"
 
motor_search_string <-
 c("dálnice", "dálniční", "silnice", "silniční", "auto", "automobil", "automobilní", "motorista", "elektrický motor", "spalovací motor", "benzín", "nafta", "dopravní nehoda") %>% str_c("\\b", ., "\\b", collapse = "|") 

# Identify UPIPE-processed chunks of interest
path_to_input_udpipe <- "~/Rprojekt/Climate/2.data_transformations/data/udpipe_processed"
udpipe_chunks_path <-
 list.files(
  path = file.path(path_to_input_udpipe),
  pattern = "*.rds",
  full.names = TRUE
 )

# Specify a function to extract doc_ids of articles with match
get_motor_articles <- function(udpipe_chunk_path) {
 tryCatch({
  readRDS(udpipe_chunk_path) %>%
   mutate(doc_id,
       text = str_to_lower(lemma, locale = "cs"),
       .keep = "none") %>%
   group_by(doc_id) %>%
   summarize(
    text = str_flatten(text, collapse = " ", na.rm = TRUE),
    motor_string_matches = str_c(unlist(
     str_extract_all(text, motor_search_string)
    ), collapse = " | ")
   ) %>%
   ungroup() %>%
   filter(nchar(motor_string_matches) > 0) %>%
   select(doc_id, motor_string_matches)
 }, error = function(e) {
  message("Error processing file: ", udpipe_chunk_path)
  message("Error message: ", e$message)
  return(NULL)
 })
}

```
# Iterate over the list of UDPIPE chunks and extract all of the documents that match the search string
```{r Iterate over Udpipe chunks to extract all motor strings}
if (Sys.info()[['sysname']] == "Windows") {
motor_article_ids <- lapply(udpipe_chunks_path, get_motor_articles) %>% bind_rows()
} else {
motor_article_ids <- mclapply(udpipe_chunks_path, get_motor_articles, mc.cores = detectCores() - 2) %>% bind_rows()
}

saveRDS(motor_article_ids, "~/Rprojekt/Climate/2.data_transformations/data/motor_sub_corpus/motor_article_ids.rds")
```

#Final step: Export sub-corpus with texts to upload to Google Sheets for manual annotation and review, while filtering out the articles, which were already manually labelled as irrelevant in the sub-corpus V2.
```{r Export motor subcorpus}
motor_article_ids <- readRDS("~/Rprojekt/Climate/2.data_transformations/data/motor_sub_corpus/motor_article_ids.rds")
path_to_input_regex <- "~/Rprojekt/Climate/2.data_transformations/data/regex_processed"
regex_chunks_path <-
 list.files(
  path = file.path(path_to_input_regex),
  pattern = "*.rds",
  full.names = TRUE
 )

# Specify function, which will extract the texts of interest based on relevant doc_ids
get_motor_texts <-
 function(regex_chunk_path,
      #doc_ids_to_remove,
      motor_article_ids) {
  regex_chunk_path %>%
   readRDS() %>%
   #filter(!article_id %in% doc_ids_to_remove) %>%
   inner_join(motor_article_ids, by = c("article_id" = "doc_id"))
 }
```

# Iterate over the list of Regex chunks and get all of the relevant texts
```{r Get all relevant motorist texts}
if (Sys.info()[['sysname']] == "Windows") {
 motor_corpus <-
  lapply(regex_chunks_path, function(x)
   get_motor_texts(x, motor_article_ids)) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
} else {
 # If not Linux - non-parallelized lapply
 motor_corpus <-
  mclapply(regex_chunks_path, function(x)
   get_motor_texts(x, motor_article_ids), mc.cores = detectCores() - 2) %>% bind_rows() #Add , doc_ids_to_remove after x, is necessary
}

# Save final SIC sub-corpus
saveRDS(motor_corpus, "~/Rprojekt/Climate/2.data_transformations/data/motor_sub_corpus/motor_corpusv2.rds")
```
# Prepare the file for Google Sheets upload
```{r prepare motorists corpus for offline reading}
# We probably need to observe the Google Sheets 50k character limit, otherwise the text of the article will not appear at all.
motor_corpus_truncated <- motor_corpus %>% 
 mutate(text = str_trunc(str_squish(text), width = 49997, side = "right", ellipsis = "..."))
 
# Save the sub-corpus to a CSV file, which we upload to Google Sheets for manual annotation and review
write_csv(motor_corpus_truncated, "~/Rprojekt/Climate/2.data_transformations/data/motor_sub_corpus/motor_articles_v2_truncated.csv")
```
